A Data Restore Model\\ for Reproducibility in Computational Statistics

### 2013-05-06 paper-data-restore-model.tex
using sweave

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

<<preliminaries, echo=FALSE, results=hide>>=
#library("lattice")
#library("MASS")
#library("lmtest")
#library("sandwich")
library(ddocks)

options(prompt = "R> ", width=10, continue = "+  ", digits = 4, show.signif.stars = FALSE)
cleanup <- FALSE
@

@@

We run this procedure for the two data templates we have generated earlier
<<results=hide>>=
ddocks_restore(
  file("./data-templates/data.dj.ddocks"), 
  targetfile="data.dj")
@

<<results=hide>>= 
ddocks_restore(
  file("./data-templates/rk.raw.ddocks"), 
  targetfile="rk.raw")
@
and reproduce the data files on the local file system.
\textit{ddocks} takes these files as a cache and skips when the restore command is run again, so that the data does not have to be reconstructed every time the code is executed.
Researchers could embed these calls within their source code to load the data by template at the beginning of their analyses and leave it there without being bothered.
%This allows us to comfortably use the code within the source code of a research project from the begin
%
%
%\begin{quote}

@@

For a basic proof of concept we have to show that the restored files equal their originals on character level.
If the two expressions
<<>>=
all.equal(
  readLines("data.dj"), 
  readLines("koenker-zeileis-09/data.dj"))

all.equal(
  readLines("rk.raw"), 
  readLines("koenker-zeileis-09/rk.raw")) 
@
evaluate to TRUE we have successfully validated the approach in terms of functionality.

>>>>

\usepackage{Sweave}
\begin{document}
\input{paper-data-restore-model-concordance}

@@

@@

We run this procedure for the two data templates we have generated earlier
\begin{Schunk}
\begin{Sinput}
R> ddocks_restore(
+    file("./data-templates/data.dj.ddocks"), 
+    targetfile="data.dj")
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
R> ddocks_restore(
+    file("./data-templates/rk.raw.ddocks"), 
+    targetfile="rk.raw")
\end{Sinput}
\end{Schunk}
and reproduce the data files on the local file system.
\textit{ddocks} takes these files as a cache and skips when the restore command is run again, so that the data does not have to be reconstructed every time the code is executed.
Researchers could embed these calls within their source code to load the data by template at the beginning of their analyses and leave it there without being bothered.
%This allows us to comfortably use the code within the source code of a research project from the begin
%
%
%\begin{quote}

@@

For a basic proof of concept we have to show that the restored files equal their originals on character level.
If the two expressions
\begin{Schunk}
\begin{Sinput}
R> all.equal(
+    readLines("data.dj"), 
+    readLines("koenker-zeileis-09/data.dj")) 
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\begin{Sinput}
R> all.equal(
+    readLines("rk.raw"), 
+    readLines("koenker-zeileis-09/rk.raw")) 
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}
evaluate to TRUE we have successfully validated the approach in terms of functionality.
